Boundary Labeling for annotated documents

### 2017-11-01 LaTeX/Paper.tex
Paper: Polished Section 2, added image showing the routing graph. Program: Added Debug variable 'hideLeaders'.

In our algorithm, the focus was put on keeping the text as readable as possible. This means that leaders aren't allowed to pass through words, which was simplified by enclosing each word in a bounding rectangle that leaders aren't allowed to pass through.
The leaders should also be kept as short as possible, so we restricted them to always be moving toward the label in at least one dimension.%Wie drücke ich das als Formel aus?
We also wanted to use the space available in the labeling area as efficiently as possible, so labels are placed as far up as possible in order to maximize the space available to future labels at the cost of possibly increased leader length.

%\subsection{Algorithm}%''Underlying Algorithm''?
To easily create leaders that exclusively use the space not taken up by a word's bounding rectangle, we decided to use a graph similar to the one Loose \cite{Loose2015} used.
As each vertex represents a physical location, they will have co-ordinates associated with them, and the vertices representing the sites will hold additional information regarding its leader and label. 
The graph is constructed by placing vertices in the space between lines next to each corner of a word's bounding rectangle, with two consecutive words in a line sharing the two vertices associated with their adjacent corners. %Insert picture
For the sites, we inserted an additional vertex above the center of the word, which will serve as the leader's starting point. After placing all vertices, we created edges between each vertex and the closest horizontal neighbour to both sides, and between nodes that are located exactly above or below each other, and exactly one line apart.

In our labeling algorithm, we decided to work through the labels in the order they appear in the text, and placing each as far up as possible, skipping any label that would've required us to move a lower line. We also opted to use fixed ports located in the top left corner of each label, as this allowed us to unabiguously place annotations by only knowing their port location, which is equal to their leader's ending point. To not restrict the label's placement by the line spacing, we left a buffer zone between the text area and the label area, which allows to place labels even further above to optimally use the available space.
The routing was implemented using a depth-first search algorithm, restricted to only selecting vertices located above or to the right of the current vertex, prioritizimg locations above whenever possible. After the algorithm terminates, it returns a path from the site to the right text border and information on where to draw the OPO-segment that connects the text area with the label's port, if successful.

>>>>

In our algorithm, the focus was put on keeping the text as readable as possible. This means that leaders aren't allowed to pass through words, which was implemented by enclosing each word in a bounding rectangle that leaders aren't allowed to pass through.
The leaders should also be kept as short as possible, so we restricted them to always be moving toward the label, even if the direct route is unavailable.%Wie drücke ich das als Formel aus?
We also wanted to use the space available in the labeling area as efficiently as possible, so labels are placed as far up as possible in order to maximize the space available to future labels at the cost of increased leader length.

\begin{figure}%{r}{0.35\textwidth}
 \captionsetup{justification=centering, margin=0.75cm}
 \centering
  \includegraphics[scale=1.0]{RoutingGraphPartial_NoBorders.png}
  \caption{Visual representation of the routing graph. The highlighted nodes represent leader sources.}
 \label{fig:RGraph}
\end{figure}
To create leaders that exclusively use the space not taken up by a word's bounding rectangle, we decided to use a graph similar to the one Loose \cite{Loose2015} used.
As each vertex represents a physical location, they will have co-ordinates associated with them, and the vertices representing the sites will hold additional information regarding its leader and label. 
The graph is constructed by placing vertices between the lines, located next to each corner of a word's bounding rectangle, with two consecutive words in a line sharing the two vertices associated with their adjacent corners. %Insert picture
For the sites, we inserted an additional vertex above the center of the word, which will serve as the leader's starting point. After placing all vertices, we created edges between each vertex and the closest horizontal neighbour to both sides, and between nodes that are located exactly above or below each other, and exactly one line apart. (For a visual representation, see Fig.~\ref{fig:RGraph})

In our labeling algorithm, we decided to work through the labels in the order they appear in the text, placing each as far up as possible, and skipping any label that would've required us place the label below its leader's source node. We also opted to use fixed ports located in the top left corner of each label, as this allowed us to unabiguously place annotations by only knowing their port location, which is equal to their leader's ending point. To not restrict the label's placement by the line spacing, we left a buffer zone between the text area and the label area, which allows us to place labels even further above to optimally use the available space.
The routing was implemented using a depth-first search algorithm, restricted to only selecting vertices located above or to the right of the current vertex, prioritizimg locations above whenever possible. After the algorithm terminates, it returns a path from the site to the right text border and information on where to draw the OPO-segment that connects the text area with the label's port, if successful.
